---
title: "esm206_lab7"
author: "Katheryn Moya"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(modelsummary)
library(stargazer)
```


## Explore penguins

```{r}

ggpairs(penguins)
#tells you the different variations of graphs that you can show your variable through
```

That's kind of overkill. Let's simplify the variables that we include in our ggpairs plot:
- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>%  #colon keeps the whole sequence in the range
  ggpairs(aes(color = species))

```
  Scatterplots are allowing us to explore the multivariate relationships between any two variables
  when you look at these relationships between these continuous variables and the other ones, does it look like a linear relationship would make sense?
  
## Multiple linear regression

We are going to try to understand (a bit better) relationships between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:
- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on only flipper length and bill depth (bad idea... there are more important variables missing)
- based on the ggpairs, can influence the variables that you choose to use in your models

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins) #need to add dataset at the end

# Call model by name to return only coefficients
model_1

# gives y intercept and coefficients for both variables - gives you the equation
# 54.14 for every increase in by 1 mm, we expect on average for  if everything else stays constant  

# More information on the coefficients and model:

summary(model_1)
```
If everything else is held constant, we expect that for each 1mm increase in flipper length, penguin body mass increases by 51.54 g, on average

8% chance we could've gotten a coefficient at least as different as the one we got - retaining null hypothesis

what does .7596 mean for this model == 76% of variants in penguin body mass is explained by this model(which contains these two variables)/ penguin flipper length and bill depth
  means that 24% of the variance is not explained by these variables
  is this good or bad? NEITHER, it is what it is
Actually, I don't think that this is an actually good model because other variables have a greater impact on penguin body mass

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + sex + species, data = penguins)

#find out coefficients
model_2


```

What has R assigned as the reference level penguin species -- adelie was assigned 0, female as sex

try interpreting the coefficients for:
flipper length, gentoo, and male

For every male, we expect that penguin body mass increases by 530.4 g, on average larger than a female given that everything else is held constant

## Visualize this models

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~ sex)
```

## A couple ways to get & report MLR model outcomes

use broom:`tidy()` to get the model coefficient info in a tidy data frame.

```{r}
penguin_model_2_coef <- tidy(model_2)
penguin_model_2_coef
```

 Try to write inline code `r` that spits out the coefficietn for Gentoo.
 
 `r penguin_model_2_coef$estimate[4]` 
 
 [4] is for the fourth variable
 
 ## Look at model diagnostics
 
 Use the plot() functon
 
```{r}
plot(model_2)
```
 
 
Use modelsummary()
```{r}
modelsummary(model_2)
```
 
 Use stargazer:
 
```{r, results = "asis"}
# this lets handock know the outcome of this code is already in html

stargazer(model_2, type = "html")
```
 
 